---
title: "Pediatric cardiologists"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: word_document
editor_options:
  chunk_output_type: console
---


```{r global options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = NA, fig.height = 15, fig.width = 15)
```


```{r}
# imp links

# https://github.com/wmurphyrd/MultipleResponseR a nice function for plotting multiple response variables
```


```{r}

library(funModeling)
library(flextable)
library(questionr)
library(tidyverse)
library(gtsummary)
library(janitor)
library(readxl)
library(labelled)
library(splitstackshape)

multi.freq.table = function(data, sep="", dropzero=FALSE, clean=TRUE) {
  # Takes boolean multiple-response data and tabulates it according
  #   to the possible combinations of each variable.
  #
  # See: http://stackoverflow.com/q/11348391/1270695

  counts = data.frame(table(data))
  N = ncol(counts)
  counts$Combn = apply(counts[-N] == 1, 1, 
                       function(x) paste(names(counts[-N])[x],
                                         collapse=sep))
  if (isTRUE(dropzero)) {
    counts = counts[counts$Freq != 0, ]
  } else if (!isTRUE(dropzero)) {
    counts = counts
  }
  if (isTRUE(clean)) {
    counts = data.frame(Combn = counts$Combn, Freq = counts$Freq)
  } 
  counts
}


data <- read_excel("data/excel.xlsx")

names(data) <- make.names(names(data),unique = T)

#funModeling::freq(data)

rmdtbl <- function(df){
  
tbl_alpha <- autofit(theme_vanilla(flextable(df)))

tbl_alpha <- bg(tbl_alpha, bg = "blue", part = "header")
tbl_alpha <- color(tbl_alpha, color = "white", part = "header")

bes <- align(tbl_alpha, align = "center")

bes <- align_text_col(bes, align = "center")
return(bes)

}

```

```{r cleaning}
#table(data$Country.of.Practice...Multiple.responses.enabled.)

# data <- data %>%
#   mutate(country = country$Country_of_practice) %>% 
#   filter(country == "Egypt", !is.na(Degree)) %>% 
#   mutate(country = ifelse(Country.of.Practice...Multiple.responses.enabled. == "Egypt", "Egypt only", "Egypt and others"))

#data$country <- fct_lump_min(data$country, 3)

```


# Table 1 Participants' demographics

```{r}
tbl1_sum <- data %>% 
  dplyr::select(Age., Gender., Job.Title., Specialty., Highest.degree.attained...If.you.choose..other...please.specify., Years.of.experience.in.Pediatric.Cardiology...Cardiac.Surgery., Country.of.Practice...Multiple.responses.enabled.)


tbl_summary(tbl1_sum, missing = "no")  %>% bold_labels() %>% italicize_levels() %>% gtsummary::as_flextable() 

```


# Table 2 

```{r}
tbl2_sum <- data %>% 
  dplyr::select(X.When.do.you.usually.ASSESS.oral.health., What.type.of.dental.specialty.would.your.refer.a.patient.to.,
                X.In.which.practice.setting.do.you.usually.refer.a.patient.at.risk.of.infective.endocarditis.for.oral.health.assessment.BEFORE.cardiac.surgeries.,
                When.do.you.usually.refer.a.patient.before.a.cardiac.surgery.,
                Have.you.ever.had.a.cardiac.surgery.cancelled.postponed.due.to.oral.infection.,
                Have.you.ever.encountered.Infective.endocarditis.from.oral.origin.,
                What.guidelines.do.you.follow.for.prevention.of.infective.endocarditis.,
                What.do.you.think.is.the.risk.of.having.tooth.decay.in.children.with.heart.diseases.compared.to.healthy.children., 
                Do.you.wish.to.be.offered.oral.health.education.related.to.your.field.of.practice.,
                How.do.you.usually.prescribe.an.antibiotic.prophylaxis.before.invasive..dental.procedures.,generic.name, 
                Antibiotic.category)



tbl_summary(tbl2_sum, missing = "no")  %>% add_n %>% bold_labels() %>% italicize_levels() %>% gtsummary::as_flextable() 

```


Next I will present the tables for the questions that have multiple response enabled. For now, these questions will not be grouped together as I am waiting for the grouping question to be determined.

#### According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.

```{r}
foo1 <- data %>% 
  select(According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.)

fes1 <- cSplit_e(foo1, 'According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.', ',', type= 'character', fill=0, drop=T)

cause <- data.frame(multi.table(fes1))

cause <- rownames_to_column(cause)

cause$rowname <- str_replace_all(cause$rowname, "According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled._", "")

cause$rowname <- fct_collapse(cause$rowname, 
                  "Chewing - Tooth brushing" = c("Chewing.", "Tooth brushing."),
                  "Invasive dental treatments" = c("Invasive dental treatments ( eg. surgeries)", "Invasive dental treatments."))

cause <- cause %>% 
  group_by(rowname) %>% 
  summarise(n = sum(n))

names(cause) <- c("Endocarditis cause", "N")


rmdtbl(cause)


# mltp_one_ques <- function(mrv, title, title_und, name){ 
#   
#   # converts a multiple response question to a summary table 
#   
#   foo1 <- data %>% 
#   select(!!mrv)
#   
#   fes1 <- cSplit_e(foo1, title, ',', type= 'character', fill=0, drop=T)
#   
#   df <- data.frame(multi.table(fes1))
#   
#   df <- rownames_to_column(df)
#   df$rowname <- str_replace_all(df$rowname, title_und, "")
#   
#   names(cause) <- c(name, "N")
#  
#   return (cause)
#   #rmdtbl(cause)
# 
# }  
# 
# cause <- mltp_one_ques(quo(According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.), "According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.", "According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled.", "cause")


# cause$rowname <- str_replace_all(cause$rowname, "According.to.your.knowledge..Infective.endocarditis.of.oral.origin.can.be.caused.by...Multiple.responses.enabled._", "")
# 
# 
#   df1 <- data %>% 
#   dplyr::select(!!mrv, !!gpvar) %>% cSplit_e(1, ',', type= 'character', fill=0, drop=T)
# names(df1) <-  sub('.*_', '', names(df1))
# 
# df2 <- data.frame(cross.multi.table(df1[,names(df1)[2:length(names(df1))]], 
#                   normal_var, true.codes=list("Y"), freq=T, tfreq="row", n=T, digits = 0)) 
# df2 <- df2 %>% 
#   rownames_to_column()
#   
# return(df2)
# }
# 


# inf_cause <- mresp_gnrl(quo(ie_cause), quo(Years.of.experience.in.pediatric.dentistry), data$Years.of.experience.in.pediatric.dentistry)


```

#### What.is..are.the.source.s..of.your.oral.health.knowledge...Multiple.responses.enabled..

```{r}
foo1 <- data %>% 
  select(What.is..are.the.source.s..of.your.oral.health.knowledge...Multiple.responses.enabled..)

fes1 <- cSplit_e(foo1, 'What.is..are.the.source.s..of.your.oral.health.knowledge...Multiple.responses.enabled..', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "What.is..are.the.source.s..of.your.oral.health.knowledge...Multiple.responses.enabled.._", "")


g$rowname <-  fct_collapse(g$rowname,
                           "medical sources,eg websites and conferences" = 
                             c("Dental websites.", "Medical conferences.", "Medical websites.")) 
info_source <- g %>% 
  group_by(rowname) %>% 
  summarise(N = sum(n))

names(info_source) <- c("Knowledge source", "N")

rmdtbl(info_source)
```


#### When.do.you.usually.REFER.a.child.with.a.congenital.heart.disease.for.oral.health.assessment.by.a.dentist.....Multiple.responses.enabled.

```{r}

foo1 <- data %>% 
  select(When.do.you.usually.REFER.a.child.with.a.congenital.heart.disease.for.oral.health.assessment.by.a.dentist.....Multiple.responses.enabled.)

fes1 <- cSplit_e(foo1, 'When.do.you.usually.REFER.a.child.with.a.congenital.heart.disease.for.oral.health.assessment.by.a.dentist.....Multiple.responses.enabled.', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "When.do.you.usually.REFER.a.child.with.a.congenital.heart.disease.for.oral.health.assessment.by.a.dentist.....Multiple.responses.enabled._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("When to refer to a dentist", "N")

rmdtbl(g)
```

#### Type.of.Medical.practice...Multiple.responses.enabled._

```{r}

foo1 <- data %>% 
  select(Type.of.Medical.practice...Multiple.responses.enabled.)

fes1 <- cSplit_e(foo1, 'Type.of.Medical.practice...Multiple.responses.enabled.', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "Type.of.Medical.practice...Multiple.responses.enabled._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("Type of medical practice", "N")

rmdtbl(g)
```


#### What.are.the.reason.s..for.not.checking.oral.health.regularly....Multiple.responses.enabled

```{r}
foo1 <- data %>% 
  select(What.are.the.reason.s..for.not.checking.oral.health.regularly....Multiple.responses.enabled..)

fes1 <- cSplit_e(foo1, 'What.are.the.reason.s..for.not.checking.oral.health.regularly....Multiple.responses.enabled..', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "What.are.the.reason.s..for.not.checking.oral.health.regularly....Multiple.responses.enabled.._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("Reasons for not checking oral health regularly", "N")

rmdtbl(g)
```


#### What.are.the.oral.health.issues.that.you.usually.discuss.with.your.patients...Multiple.responses.enabled..


```{r}
foo1 <- data %>% 
  select(What.are.the.oral.health.issues.that.you.usually.discuss.with.your.patients...Multiple.responses.enabled..)

fes1 <- cSplit_e(foo1, 'What.are.the.oral.health.issues.that.you.usually.discuss.with.your.patients...Multiple.responses.enabled..', ',', type= 'character', fill=0, drop=T)


g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "What.are.the.oral.health.issues.that.you.usually.discuss.with.your.patients...Multiple.responses.enabled.._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("Oral health issues discussed with patients", "N")

rmdtbl(g)

```

#### How.usually.a.tooth.decay.looks.like...Multiple.responses.enabled.

```{r}
foo1 <- data %>% 
  select(How.usually.a.tooth.decay.looks.like...Multiple.responses.enabled.)

fes1 <- cSplit_e(foo1, 'How.usually.a.tooth.decay.looks.like...Multiple.responses.enabled.', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes1))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "How.usually.a.tooth.decay.looks.like...Multiple.responses.enabled._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("Tooth decay appearance", "N")

rmdtbl(g)


```

#### For whom do you usually prescribe prophylactic antibiotics before invasive dental procedures Multiple responses enabled  


```{r}
foo <- data %>% 
  select(For.whom.do.you.usually.prescribe.prophylactic.antibiotics.before.invasive.dental.procedures...Multiple.responses.enabled..)

fes <- cSplit_e(foo, 'For.whom.do.you.usually.prescribe.prophylactic.antibiotics.before.invasive.dental.procedures...Multiple.responses.enabled..', ',', type= 'character', fill=0, drop=T)

g <- data.frame(multi.table(fes))

g <- rownames_to_column(g)

g$rowname <- str_replace_all(g$rowname, "For.whom.do.you.usually.prescribe.prophylactic.antibiotics.before.invasive.dental.procedures...Multiple.responses.enabled.._", "")

g <- g %>% 
  dplyr::select(-X.multi)

names(g) <- c("Prophylactic antibiotic precribed to", "N")
3
rmdtbl(g)
```

